Positional surprisal (1-3grams) in CHILDES corpora

### 2019-05-07 process_bnc.Rmd
bnc & switchboard surprisals

```{r load_libraries}
library(tidyverse)
library(stringr)
library(feather)
library(here)

@@

```{r parse_bnc, eval = F}  
files <- list.files(here("BNC/Texts"), "*.xml", full.names = T, recursive = T)

@@

  system(paste0("xsltproc BNC/XML/Scripts/justTheWords.xsl ", file, " > ", newname))
}

map(files, parse_BNC)

write_feather(txt, "switchboard/switchboard.feather")
```

@@

```{r post_process_bnc}
bnc_tokens <- read_feather(here("../bnc/bnc.feather")) %>%
  mutate(length = str_count(value, pattern = " +") + 1) %>% 
  mutate(utterance_id = 1:n()) %>%
  unnest_tokens(word, value, token = stringr::str_split, pattern = " +") %>%
  group_by(utterance_id) %>%
  mutate(word_order = 1:n())

>>>>

```{r load_libraries}
library(tidyverse)
library(stringr)
library(feather)
library(here)
library(tidytext)

@@

You want to download the file from (http://ota.ox.ac.uk/desc/2554). Move it to the same directory as this .Rmd file

```{r parse_bnc, eval = F}

files <- list.files(here("bnc/Texts"), "*.xml", full.names = T, recursive = T)

@@

  system(paste0("xsltproc bnc/XML/Scripts/justTheWords.xsl ", file, " > ", newname))
}

map(files, parse_BNC)
```

@@

```{r post_process_bnc}
bnc_tokens <- read_feather(here("bnc/bnc.feather")) %>%
  mutate(length = str_count(value, pattern = " +") + 1) %>% 
  mutate(utterance_id = 1:n()) %>%
  unnest_tokens(word, value, token = stringr::str_split, pattern = "[ +]+") %>%
  group_by(utterance_id) %>%
  mutate(word_order = 1:n())

### 2019-05-07 surprisal/childes_surprisal.Rmd
bnc & switchboard surprisals

Get utterances
```{r get_utterances}
prov_utterances <- get_utterances(corpus = "Providence") #stem or gloss
zhou_utterances <- get_utterances(corpus = "ZhouDinner")
```

```{r}
adult_utterances <- zhou_utterances %>%
  filter(speaker_role == "Target_Child") %>% 
  mutate(length = str_count(gloss, pattern = "[ +]+") + 1) %>%
  mutate(utterance_id = 1:n()) %>%
  unnest_tokens(word, stem) %>%
  group_by(utterance_id) %>%
  mutate(word_order = 1:n())
```

>>>>

Get utterances
```{r get_utterances}
prov_utterances <- get_utterances(corpus = "Providence") #stem or gloss
zhou_utterances <- get_utterances(corpus = "ZhouDinner") #stem for pinyin
```

```{r}
adult_utterances <- prov_utterances %>%
  filter(speaker_role == "Target_Child") %>% 
  mutate(length = str_count(stem, pattern = "[ +]+") + 1) %>%
  mutate(utterance_id = 1:n()) %>%
  unnest_tokens(word, stem, token = stringr::str_split, pattern = "[ +]+") %>%
  group_by(utterance_id) %>%
  mutate(word_order = 1:n())
```
